Co-moving stars in \textsl{Gaia DR1}: a catalog of genuine comoving star pairs from low-resolution spectroscopic follow-up

### 2017-06-03 paper/comoving-followup.tex
TODOs for the future

TODO: Comparing repeat visits on subsequent nights, absolute errors ~20 km/s

@@

TODO:
- Plot of magnitude of 3d velocity difference vs. 3d separation (inferred).

@@

@@

@@

- Orbits of true pairs in the Galaxy, any halo or thick-disk?

>>>>

% \begin{figure}[htbp]
%   \begin{center}
%     \includegraphics[width=\linewidth]{placeholder.pdf}
%   \end{center}
%   \caption{%
%     \todo{Some summary plots about the MCMC fits...}
%     \label{fig:Halpha-mcmc}}
% \end{figure}

TODO: Comparing repeat visits on subsequent nights, absolute errors ~20 km/s
- How many of our targets already have measurements in Simbad?

% \begin{figure}[htbp]
%   \begin{center}
%     \includegraphics[width=\linewidth]{placeholder.pdf}
%   \end{center}
%   \caption{%
%     \todo{Plot showing my RV's vs. previously measured.}
%     \label{fig:compare-previous}}
% \end{figure}

@@

@@

TODO: 10 overlap with Shaya and Olling

TODO: Do I want to do isochrone fitting for all of them?

@@

TODO: Plot of magnitude of 3d velocity difference vs. 3d separation (inferred).

TODO: separation distribution - combine with Shaya and Olling sample!

TODO: distribution of orbital poles in Galactic coordinates

@@

TODO: Orbits of true pairs in the Galaxy, any halo or thick-disk?

\section{Discussion}

Abundances!
